---
title: "ATP Analysis"
description: |
  Welcome to the website. I hope you enjoy it!
site: distill::distill_website
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(rmarkdown)
library(gt)
```
# Background
The [Association of Tennis Professionals](https://www.atptour.com/en/corporate/about) is "the global governing body of men’s professional tennis" and was created in 1972. Using data compiled from [Jeff Sackman's Github Repository](https://github.com/JeffSackmann/tennis_atp), this project looks at some of the trends in the game since its conception.  

# Process & Methodology
The website was created using the distill R package.

Data wrangling and visualization utilized the tidyverse R package.

Looking at just single's matches, the data needed to be compiled from annual datasets into a single document.

## Aggregated  Raw Data
```{r table}
table <- read_rds("aggregate_data.rds") %>% select(-source)
paged_table(table, options(cols.print = 12))
```

# Analysis: How the Game Has Changed
## Aces over the years
```{r ace-plot, echo = FALSE}
ace_plot <- read_rds("plot_ace_total_and_surface.rds")
ace_plot
```
### Comments
Carpet surface matches were officially ended on the ATP Tour in 2009.

The different properties of each type of court surface largely account for the inter-surface difference in ace rates.

As rackets have gotten more powerful, the ace rate has also increased.

## Average Age at the Grand Slams
```{r age_plot}
age_plot <- read_rds("plot_avg_age_combined.rds")
age_plot
```
### Comments
An aging generation is making its way through the Grand Slam series. Looking beyond the Big Three (Roger Federer, Rafael Nadal and Novak Djokovic), a new generation seems to be on its way.

## Average Height at Grand Slams
```{r height_plot}
height_plot <- read_rds("plot_avg_ht.rds")
height_plot
```
### Comments
A height advantage brings a competitive edge of the game, which more taller athletes have been able to take advantage of.